Topology and experimental distinguishability

### 2017-08-07 Articles/TopologyAndExperimentalDistinguishability/article.tex
Added reference to Basener textbook
Removing "Submitted" footnote
Addressing observation from Mayer

@@

The successful use of mathematical ideas in experimental sciences is long established and celebrated~\cite{wigner}. Topology is perhaps the most widespread, either directly~\cite{rashevsky, chichilnisky} or as a foundation to other tools~\cite{nakahara}.  This leads one to ask, why is it so successful? What property is captured by topological spaces that is so fundamental for scientific investigation?

@@

@@

We hope that this work, because of both its method and result, can provide a more solid foundation to formalize experimental sciences.

>>>>

% Temporary to remove "submitted to"
\makeatletter
\def\ps@pprintTitle{%
	\let\@oddhead\@empty
	\let\@evenhead\@empty
	\def\@oddfoot{}%
	\let\@evenfoot\@oddfoot}
\makeatother

@@

The successful use of mathematical ideas in experimental sciences is long established and celebrated~\cite{wigner}. Topology is perhaps the most widespread, either directly~\cite{rashevsky, chichilnisky} or as a foundation to other tools~\cite{nakahara, basener}.  This leads one to ask, why is it so successful? What property is captured by topological spaces that is so fundamental for scientific investigation?

@@

\begin{proof}
	We need to show that the basis-to-basis topology is a topology. By definition, it is closed under finite intersection and arbitrary union. The set $V(X,\emptyset)$ is in the topology and contains no functions.  The set $V(X,Y)$ is in the topology and contains all functions.
\end{proof}

@@

In light of this work, the effectiveness of mathematics in the natural sciences is perhaps not so unreasonable. We hope that the methods and results shown here can provide a more solid foundation to formalize experimental sciences.
